Halving the cost of quantum addition

### 2017-10-05 paper.tex
Move figures to end of paper in own section
Abbreviated bibliography and dropped figure files to be inline

\documentclass[twocolumn]{revtex4-1}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[pdfpagelabels,pdftex,bookmarks,breaklinks]{hyperref}
\usepackage{tikz}
\usepackage[all]{hypcap}
\hypersetup{colorlinks,citecolor=blue,urlcolor=blue,linkcolor=blue}

@@

@@

\begin{figure}
  \includegraphics[width=\linewidth]{figures/adder.pdf}
  \caption{
	A 5-bit adder with T-count of 16.
	Uses Clifford operations, four logical-AND computations each with a T-count of 4, and four logical-AND erasures requiring no T gates.
	Generalizes to an $n$-bit adder with a T-count of $4n - 4$.
	See \autoref{fig:adder-building-block} for the adder building-block and \autoref{fig:temporary-logical-AND} for the logical-AND computation and uncomputation circuits.
  }
  \label{fig:adder}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\linewidth]{figures/adder-building-block.pdf}
  \caption{
	Our adder circuit building-block, with a T-count of 4.
	A variant of the Cuccaro adder building-block \citep{Cuccaro2004}.
  }
  \label{fig:adder-building-block}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\linewidth]{figures/temporary-logical-and.pdf}
  \caption{
	How to compute and uncompute the logical-AND of two qubits.
	The computation circuit (top) has a T-count of 4 and a T-depth of 1.
	Note that the $|A\rangle$ state input contributes to the T-count, because $|A\rangle$ states are the resource used to perform T gates.
	The uncomputation circuit (bottom) uses a measure-and-fixup approach \cite{Jones2013} that requires only Clifford gates, and so has a T-count of zero.
    \\
    An alternative uncomputation construction is to simply do the reverse of the computation circuit.
    This alternative approach has a net T-count of 2 (because an $|A\rangle$ state is recovered).
    The resulting temporary logical-AND with a T-count of 6 would still be an improvement on existing work, but would be inferior to the measure-and-fixup approach shown above.
  }
  \label{fig:temporary-logical-AND}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\linewidth]{figures/other-adder-building-blocks.pdf}
  \caption{
	Variations on our adder construction.
	(a) is a controlled-adder building-block with a T-count of 8.
	The addition will only occur when the control is on.
	(b) is a temporary-adder building-block with a T-count of 4.
	Has the same T-count as a normal addition, but makes the result available before any uncomputation steps are needed.
  }
  \label{fig:other-adder-building-blocks}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\linewidth]{figures/paired-toffoli-replacement-rule.pdf}
  \caption{
	A sufficient condition for replacing a pair of Toffoli gates with a temporary logical-AND, saving 4 T gates.\\
	1) The later Toffoli gate must be uncomputing the earlier Toffoli gate.\\
	2) Intermediate operations must not be sensitive to the presence of the entangled ancilla.
  }
  \label{fig:paired-toffoli-replacement-rule}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\linewidth]{figures/synthesize-t-gates-from-temporary-logical-and.pdf}
  \caption{
	Three T gates can be synthesized by performing a temporary logical-AND, one T gate, and various Clifford operations.
	Clifford operations can't produce T gates, so the extra T gates must be coming from the temporary logical-AND.
	This proves that performing the temporary logical-AND requires at least two T gates.
  }
  \label{fig:synthesize-t-gates-from-temporary-logical-and}
\end{figure}

@@

\bibliographystyle{plainnat}
\bibliography{citations}

>>>>

\documentclass[twocolumn]{revtex4-1}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage[pdfpagelabels,pdftex,bookmarks,breaklinks]{hyperref}
\usepackage{tikz}
\usepackage[all]{hypcap}
\hypersetup{colorlinks,citecolor=blue,urlcolor=blue,linkcolor=blue}

@@

% [figure 1 "adder" was here]

@@

@@

% [figure 2 "adder-building-block" was here]

@@

% [figure 3 "temporary-logical-and" was here]

@@

% [figure 4 "other-adder-building-blocks" was here]

@@

% [figure 5 "paired-toffoli-replacement-rule" was here]

@@

% [figure 6 "synthesize-t-gates-from-temporary-logical-and" was here]

@@

\bibliographystyle{npj-quantum-information}
\bibliography{citations}

\section*{Figures}

\begin{figure}[H]
  \includegraphics[width=\linewidth]{adder.pdf}
  \caption{
	A 5-bit adder with T-count of 16.
	Uses Clifford operations, four logical-AND computations each with a T-count of 4, and four logical-AND erasures requiring no T gates.
	Generalizes to an $n$-bit adder with a T-count of $4n - 4$.
	See \autoref{fig:adder-building-block} for the adder building-block and \autoref{fig:temporary-logical-AND} for the logical-AND computation and uncomputation circuits.
  }
  \label{fig:adder}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\linewidth]{adder-building-block.pdf}
  \caption{
	Our adder circuit building-block, with a T-count of 4.
	A variant of the Cuccaro adder building-block \citep{Cuccaro2004}.
  }
  \label{fig:adder-building-block}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\linewidth]{temporary-logical-and.pdf}
  \caption{
	How to compute and uncompute the logical-AND of two qubits.
	The computation circuit (top) has a T-count of 4 and a T-depth of 1.
	Note that the $|A\rangle$ state input contributes to the T-count, because $|A\rangle$ states are the resource used to perform T gates.
	The uncomputation circuit (bottom) uses a measure-and-fixup approach \cite{Jones2013} that requires only Clifford gates, and so has a T-count of zero.
    \\
    An alternative uncomputation construction is to simply do the reverse of the computation circuit.
    This alternative approach has a net T-count of 2 (because an $|A\rangle$ state is recovered).
    The resulting temporary logical-AND with a T-count of 6 would still be an improvement on existing work, but would be inferior to the measure-and-fixup approach shown above.
  }
  \label{fig:temporary-logical-AND}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{other-adder-building-blocks.pdf}
  \caption{
	Variations on our adder construction.
	(a) is a controlled-adder building-block with a T-count of 8.
	The addition will only occur when the control is on.
	(b) is a temporary-adder building-block with a T-count of 4.
	Has the same T-count as a normal addition, but makes the result available before any uncomputation steps are needed.
  }
  \label{fig:other-adder-building-blocks}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{paired-toffoli-replacement-rule.pdf}
  \caption{
	A sufficient condition for replacing a pair of Toffoli gates with a temporary logical-AND, saving 4 T gates.\\
	1) The later Toffoli gate must be uncomputing the earlier Toffoli gate.\\
	2) Intermediate operations must not be sensitive to the presence of the entangled ancilla.
  }
  \label{fig:paired-toffoli-replacement-rule}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{synthesize-t-gates-from-temporary-logical-and.pdf}
  \caption{
	Three T gates can be synthesized by performing a temporary logical-AND, one T gate, and various Clifford operations.
	Clifford operations can't produce T gates, so the extra T gates must be coming from the temporary logical-AND.
	This proves that performing the temporary logical-AND requires at least two T gates.
  }
  \label{fig:synthesize-t-gates-from-temporary-logical-and}
\end{figure}
